---
title: "Stat 850 Project Report"
author: "Firstname Lastname, Firstname Lastname, ..."
format: html
editor: visual
bibliography: references.bib
---

## Introduction

Introduce your dataset and basic questions for exploration. Explain any unique approaches you will take or any interesting features of your dataset that you have to overcome. Cite the source of your dataset, and briefly discuss how it was collected.

Discuss the variables in the dataset and if there are anomalies in the variables, provide some visual assessment of the anomalies and explain how they may have arisen. You should cover most of the information in your proposal data section, but should primarily use paragraphs and not lists/tables (the exception may be a list of e.g. items which were measured).

## Methods

Describe any data cleaning and rearranging you needed to do to get your dataset into a workable form. Make sure to cite any packages which were important in your data cleaning process in this section. For instance, if you used dplyr, then it would be appropriate to say something like

> we used the group-apply-combine paradigm with the `dplyr` functions `group_by` and `summarize` [@dplyr-package] to generate a dataset for each day of the observation period from the 15-minute interval observations in the raw data set.

## Topic of Exploration

Here, you want to introduce the first topic you want to explore with your (newly cleaned up) data. Code to process data should be contained in chunks above this point, and those chunks should *not* be included in the report.

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

If you generate a figure, it should have a caption. Here's a demonstration of how to do that:

```{r iris-plot}
#| label: fig-iris
#| fig-width: 8
#| fig-height: 4 # Change the figure dimensions using fig-width/height
#| out-width: 80% # This changes the size of the figure as rendered in the text. 
#| fig-cap: "This figure shows the relationship between sepal width and petal width in irises. I've used geom_jitter to combat overplotting, as the data are measured in relatively consistent increments. The figure is drawn with `ggplot2` [@ggplot2-package]."
#| echo: false


data(iris)
library(ggplot2)
ggplot(iris, aes(x = Sepal.Width, y = Petal.Width, color = Species)) + 
  geom_jitter() + 
  xlab("Sepal Width (cm)") + ylab("Petal Width (cm)") + 
  ggtitle("Sepal and Petal Dimensions")
```

Then, you can reference @fig-iris in the text and the appropriate cross-reference will be generated.

You can find additional information about formatting figures generated from code in the [quarto documentation](https://quarto.org/docs/authoring/figures.html#computations).

## Conclusion

Here, you want to summarize the main points of what you've learned from this investigation, in paragraph form.

## Tips

(delete this section from your report!)

Almost anything you might want to know about how to format output in quarto can be found [here](https://quarto.org/docs/authoring/markdown-basics.html). Feel free to email/come to office hours to figure out how to do XYZ - part of the goal of making you write this report is that I want you to know how to write e.g. a journal paper in Quarto as well, so now's the time to experiment.

If you want to know what the wordcount of your report is, you can run the following command in your terminal:

    pandoc --lua-filter wordcount.lua report.qmd

Notice that I have not pushed `report.html` or the `report_files/` folder to github - this is intentional. If you *must*, you can push these documents right before you submit your project, but I'd far prefer it if you just let me compile these on my computer and never pushed them at all.
